My title

### 2022-03-22 outputs/paper/paper.Rmd
Add figure height for appendix images

```{r sex-crime-plot, fig.cap="Sex Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE, fig.height=6, fig.width=8}
sex_crime_plot
```

```{r culture-crime-plot, fig.cap="Ethnicity or culture Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE}
culture_crime_plot
```

```{r race-skin-crime-plot, fig.cap="Race and Skin Color Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE}
race_skin_crime_plot
```

```{r physical-appearance-crime-plot, fig.cap="Physical appearance Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE}
physical_appearance_crime_plot
```

```{r religion-crime-plot, fig.cap="Religion Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE}
religion_crime_plot
```

```{r sexual-orientation-crime-plot, fig.cap="Sexual orientation Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE}
sexual_orientation_crime_plot
```

```{r age-crime-plot, fig.cap="Age Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE}
age_crime_plot
```

```{r physical-mental-disability-crime-plot, fig.cap="Physical or mental disability Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE}
physical_mental_disability_crime_plot
```

```{r language-crime-plot, fig.cap="Language Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE}
language_crime_plot
```

```{r university-education-vs-crime, fig.width=8, fig.height=5, echo=FALSE, warning=FALSE, message = FALSE}
cross_compare_barplot(data=gss_data %>% filter(msvic < 900) %>% filter(eor_01c < 3),
                            col1 = "eor_01c", col2 = "msvic",
                      col1_num=eor_01c_num, col1_labels=eor_01c_label,
                      col2_num=msvic_num, col2_labels=msvic_labels, 
                      plot_title="University Education VS Crime",
                      plot_subtitle="",
                      plot_xlab="Crime",
                      plot_ylab="Percentage", 
                      plot_fill_lab="Education")
```

>>>>

```{r sex-crime-plot, fig.height=4, fig.cap="Sex Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE}
sex_crime_plot
```

```{r culture-crime-plot, fig.height=4, fig.cap="Ethnicity or culture Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE}
culture_crime_plot
```

```{r race-skin-crime-plot, fig.height=4, fig.cap="Race and Skin Color Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE}
race_skin_crime_plot
```

```{r physical-appearance-crime-plot, fig.height=4, fig.cap="Physical appearance Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE}
physical_appearance_crime_plot
```

```{r religion-crime-plot, fig.height=4, fig.cap="Religion Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE}
religion_crime_plot
```

```{r sexual-orientation-crime-plot, fig.height=4, fig.cap="Sexual orientation Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE}
sexual_orientation_crime_plot
```

```{r age-crime-plot, fig.height=4, fig.cap="Age Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE}
age_crime_plot
```

```{r physical-mental-disability-crime-plot, fig.height=4, fig.cap="Physical or mental disability Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE}
physical_mental_disability_crime_plot
```

```{r language-crime-plot, fig.height=4, fig.cap="Language Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE}
language_crime_plot
```

```{r university-education-vs-crime, fig.cap="University Education VS Crime", fig.width=8, fig.height=5, echo=FALSE, warning=FALSE, message = FALSE}
cross_compare_barplot(data=gss_data %>% filter(msvic < 900) %>% filter(eor_01c < 3),
                            col1 = "eor_01c", col2 = "msvic",
                      col1_num=eor_01c_num, col1_labels=eor_01c_label,
                      col2_num=msvic_num, col2_labels=msvic_labels, 
                      plot_title="University Education VS Crime",
                      plot_subtitle="",
                      plot_xlab="Crime",
                      plot_ylab="Percentage", 
                      plot_fill_lab="Education")
```
